Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-10-27 prob.tex
prob.tex Change the symbol for Radon-Nikodym derivative from f to m...

Although specifying a probability measure for every event looks complex,
it can be simply constructed by 
\begin{equation}
\pmeas(E)=\sideset{_{\mathbb{R}}}{_{\omega\in E}}\sum f(\omega)\textrm{ ,}\label{eq:Radon-Nikodym}
\end{equation}
where $f:\Omega\rightarrow[0,1]$, $\sideset{_{\mathbb{R}}}{_{\omega\in\Omega}}\sum f(\omega)=1$,
and $f$ is called the Radon-Nikodym derivative of $\pmeas$ (with
respect to the counting measure)~\cite{Nikodym1930,Folland1999}.
The converse is also valid and called the Radon-Nikodym theorem.

\begin{thm}[Radon-Nikodym theorem for finite probability space~\cite{Kolmogorov1950,Swart2013}]
For every probability measure~$\pmeas$, there exists a unique Radon-Nikodym
derivative~$f$ such that equation~(\ref{eq:Radon-Nikodym}) holds.\qed\end{thm}

For example, the Radon-Nikodym derivative of $\pmeas$ in example~\ref{ex1}
is: 
\[
\begin{array}{rcl}
f\left(HH\right)=1/3,\quad f\left(HT\right)=0,\quad f\left(TH\right)=2/3,\quad f\left(TT\right)=0\textrm{ .}\end{array}
\]

@@

In contrast to real-valued probability measures, there is no easy
Radon-Nikodym theorem to simplify an interval-valued probability measure
to its Radon-Nikodym derivative. So far, the interval-valued Radon-Nikodym
Theorems are either too restricted to apply to all interval-valued
probability measures~\cite{Choquet1954,Graf1980,Goodman1997} or
corresponding an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
to another set function~$\bar{f}:\events\rightarrow\bar{\mathscr{I}}$
which is not as simple as the original Radon-Nikodym derivative~\cite{GilboaSchmeidler1994,Goodman1997}.

@@

Mathematically, to fix the magnetic field of the Stern-Gerlach experiment
is to pick a orthonormal basis~$\Omega=\left\{ \ket{\psi_{j}}\right\} _{j=0}^{d-1}$
for a given Hilbert space~$\Hilb$ of dimension~$d$, and the state
of the silver atom can be represented by a density matrix~$\rho$
written in the same basis, i.e., $\rho=\tensor*[_{\mathscr{O}}]{\sum}{_{i=0}^{d-1}}\tensor*[_{\mathscr{O}}]{\sum}{_{i=0}^{d-1}}r_{ij}\ket{\psi_{i}}\bra{\psi_{j}}$.
As we discussed in the last paragraph, the Born rule of the mixed
state~$\rho$ induces a classical probability measure~$\pmeas^{\Omega}:2^{\Omega}\rightarrow[0,1]$
on $\Omega$. Let $E\in2^{\Omega}$ be a classical event and $P=\tensor*[_{\mathscr{O}}]{\sum}{_{\ket{\psi_{j}}\in E}}\proj{\psi_{j}}$
be the quantum event corresponding to subspace span by $E$, we can
have
\begin{equation}
\pmeas^{\Omega}\left(E\right)=\mu_{\rho}^{B}\left(P\right)\overset{\left(\ref{BornRule.mixed}\right)}{=}\Tr\left(\rho P\right)=\sideset{_{\mathbb{R}}}{_{\ket{\psi_{j}}\in E}}\sum r_{jj}\textrm{ .}\label{BornRule.mixed-1}
\end{equation}
By equation (\ref{eq:Radon-Nikodym}), the Radon-Nikodym derivative
of $\pmeas'$ is $f\left(\ket{\psi_{j}}\right)=r_{jj}$, which is
just the diagonal elements of $\rho$. In this sense, the Radon-Nikodym
derivative~$f$ is a special case of the density matrix~$\rho$,
and the Radon-Nikodym theorem is a special case of Gleason's theorem~\cite{HollandJr1970,Redhead1987-REDINA,Jaeger2007}.

>>>>

Although specifying a probability measure for every event looks complex,
it can be simply constructed by 
\begin{equation}
\pmeas(E)=\sideset{_{\mathbb{R}}}{_{\omega\in E}}\sum m(\omega)\textrm{ ,}\label{eq:Radon-Nikodym}
\end{equation}
where $m:\Omega\rightarrow[0,1]$, $\sideset{_{\mathbb{R}}}{_{\omega\in\Omega}}\sum m(\omega)=1$,
and $m$ is called the Radon-Nikodym derivative of $\pmeas$ (with
respect to the counting measure)~\cite{Nikodym1930,Folland1999}.
The converse is also valid and called the Radon-Nikodym theorem.

\begin{thm}[Radon-Nikodym theorem for finite probability space~\cite{Kolmogorov1950,Swart2013}]
For every probability measure~$\pmeas$, there exists a unique Radon-Nikodym
derivative~$m$ such that equation~(\ref{eq:Radon-Nikodym}) holds.\qed\end{thm}

For example, the Radon-Nikodym derivative of $\pmeas$ in example~\ref{ex1}
is: 
\[
\begin{array}{rcl}
m\left(HH\right)=1/3,\quad m\left(HT\right)=0,\quad m\left(TH\right)=2/3,\quad m\left(TT\right)=0\textrm{ .}\end{array}
\]

@@

In contrast to real-valued probability measures, there is no easy
Radon-Nikodym theorem to simplify an interval-valued probability measure
to its Radon-Nikodym derivative. So far, the interval-valued Radon-Nikodym
Theorems are either too restricted to apply to all interval-valued
probability measures~\cite{Choquet1954,Graf1980,Goodman1997} or
corresponding an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
to another set function~$\bar{m}:\events\rightarrow\bar{\mathscr{I}}$
which is not as simple as the original Radon-Nikodym derivative~\cite{GilboaSchmeidler1994,Goodman1997}.

@@

Mathematically, to fix the magnetic field of the Stern-Gerlach experiment
is to pick a orthonormal basis~$\Omega=\left\{ \ket{\psi_{j}}\right\} _{j=0}^{d-1}$
for a given Hilbert space~$\Hilb$ of dimension~$d$, and the state
of the silver atom can be represented by a density matrix~$\rho$
written in the same basis, i.e., $\rho=\tensor*[_{\mathscr{O}}]{\sum}{_{i=0}^{d-1}}\tensor*[_{\mathscr{O}}]{\sum}{_{i=0}^{d-1}}r_{ij}\ket{\psi_{i}}\bra{\psi_{j}}$.
As we discussed in the last paragraph, the Born rule of the mixed
state~$\rho$ induces a classical probability measure~$\pmeas^{\Omega}:2^{\Omega}\rightarrow[0,1]$
on $\Omega$. Let $E\in2^{\Omega}$ be a classical event and $P=\tensor*[_{\mathscr{O}}]{\sum}{_{\ket{\psi_{j}}\in E}}\proj{\psi_{j}}$
be the quantum event corresponding to subspace span by $E$, we can
have 
\begin{equation}
\pmeas^{\Omega}\left(E\right)=\mu_{\rho}^{B}\left(P\right)\overset{\left(\ref{BornRule.mixed}\right)}{=}\Tr\left(\rho P\right)=\sideset{_{\mathbb{R}}}{_{\ket{\psi_{j}}\in E}}\sum r_{jj}\textrm{ .}\label{BornRule.mixed-1}
\end{equation}
By equation (\ref{eq:Radon-Nikodym}), the Radon-Nikodym derivative
of $\pmeas'$ is $m\left(\ket{\psi_{j}}\right)=r_{jj}$, which is
just the diagonal elements of $\rho$. In this sense, the Radon-Nikodym
derivative~$m$ is a special case of the density matrix~$\rho$,
and the Radon-Nikodym theorem is a special case of Gleason's theorem~\cite{HollandJr1970,Redhead1987-REDINA,Jaeger2007}.
